Trajipaq_sentiment_an

### 2023-08-16 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_an.Rmd
update

v_CSD <- c("age", "education", "revenu", "sexe", "origine", "langue_mat", "statut_mat", "religion")

trajipaq <- trajipaq %>%
  filter(rowSums(!is.na(across(all_of(v_CSD)))) == length(v_CSD))
```

@@

```{r}
stargazer(
  reg_WGI_can_2021,
  reg_WGI_can_2021_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

>>>>

v_noNA <- c("age", "education", "revenu", "sexe", "origine", "langue_mat", "statut_mat", "religion", "sentimapp_can_dico", "wgi_origin_arrival_score", "wgi_arrival_diff", "wgi_origin_2021_score", "wgi_2021_diff")

trajipaq <- trajipaq %>%
  filter(rowSums(!is.na(across(all_of(v_noNA)))) == length(v_noNA))
```

@@

```{r}
 stargazer(
  reg_WGI_can_arrival,
  reg_WGI_can_arrival_ctrl,
  reg_WGI_arrival_diff,
  reg_WGI_arrival_diff_ctrl,
  reg_WGI_can_2021,
  reg_WGI_can_2021_ctrl,
  reg_WGI_2021_diff,
  reg_WGI_2021_diff,
  reg_WGI_2021_diff_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

stargazer(
  reg_WGI_can_2021,
  reg_WGI_can_2021_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)
